---
title: "Final Project"
author: "Matti Harrison"
date: "10/18/2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(janitor)

Harvard <- read_csv("Harvard- Data USA Cart.csv")

Berkeley <- read_csv("Berkeley- Data USA Cart.csv")

Oregon <- read_csv("Oregon- Data USA Cart.csv")

Wake_Forest <- read_csv("Wake Forest- Data USA Cart.csv")
```


```{r, echo=FALSE, warning= FALSE, error= FALSE, message= FALSE}
Harvard %>% 
  ggplot(aes(x=avg_wage_2014, y= num_ppl_2014)) + geom_point() + scale_y_log10()
```

##Does it matter if you choose a Private or Public University?
I want to compare the top public and private Universities to see if there is a difference in average earnings after graduation.  For my initial comparisons I will see the differences in tuition vs. debt ratio.  Then I will continue on to the most common major for each school, this usually predicts the wage.  Then I will compare the average earnings between the different schools.  

I originally wanted to get the #1 private/public university and then also the #50 school for each to be able to standardize.  #1 schools are in the top for overall school so #50 will be able to see a clear difference.  I got the original data from Data USA.
 
I am not sure if there is a way to get data from all public/private universities into 1 dataset.  

private- (1) Harvard (50) Wake Forest University

public- (1) UC Berkeley (50) University of Oregon

```{r, echo=FALSE, warning= FALSE, error= FALSE, message= FALSE}
summary(Harvard)
```



